\cvsection{Skills}
  \begin{cvskills}
    \cvskill
      {Architectural Patterns}
      {\skilltypestyle{High Proficiency:} DDD, EDA, MVC, Microservices, REST.}

    \cvskill
      {}
      {\skilltypestyle{Medium Proficiency:} CQRS.}

    \cvskill
      {Computation Models}
      {\skilltypestyle{High Proficiency:} Declarative(Functional), Stateful(Imperative), Stateful(Object-Oriented).}

    \cvskill
      {Languages}
      {\skilltypestyle{High Proficiency:} Python, Scala.}

    \cvskill
      {}
      {\skilltypestyle{Medium Proficiency:} C, Java, JavaScript, HTML.}

    \cvskill
      {}
      {\skilltypestyle{Low Proficiency:} C++, CSS.}

    \cvskill
      {Frameworks and Libraries}
      {\skilltypestyle{Medium Proficiency:} Flask, Express, Node, React, Dropwizard.}

    \cvskill
      {Database Management}
      {\skilltypestyle{High Proficiency:} SQL, TSQL.}

    \cvskill
      {}
      {\skilltypestyle{Medium Proficiency:} MS SQL Server, PostgreSQL, MySQL, Alembic, SQLAlchemy, Flyway.}

    \cvskill
      {Infrastructure and Orchestration}
      {\skilltypestyle{Medium Proficiency:} Docker, Kubernetes, RabbitMQ.}

    \cvskill
      {}
      {\skilltypestyle{Low Proficiency:} Firebase.}

    \cvskill
      {Build Automation and Testing}
      {\skilltypestyle{Medium Proficiency:} Pipenv, Pytest, sbt, ScalaTest, Jest, Make.}

    \cvskill
      {CI/CD}
      {\skilltypestyle{Medium Proficiency:} GitLab CI/CD, GitHub Actions.}

    \cvskill
      {Source Management}
      {\skilltypestyle{High Proficiency:} Git, GitLab, GitHub.}

    \cvskill
      {Process Automation}
      {\skilltypestyle{High Proficiency:} Camunda, BPMN 2.0.}

    \cvskill
      {Project Management and Documentation}
      {\skilltypestyle{High Proficiency:} Confluence, Jira.}
  \end{cvskills}
